Election Predictions:A Data-Driven Approach to US Election Forecasting

### 2024-11-04 paper/paper.qmd
Update paper.qmd

Polling is a commonly used tool to understand public opinion. However, it may lack accuracy due to various biases, such as social desirability bias, non-response bias, and sampling error. In this paper, we attempt to construct a model measures ....

@@

*Results paragraph:* Summarize the key findings of the model, highlighting its predictive accuracy and implications.

@@

Telegraphing paragraph: 
The remainder of this paper is structured as follows: Section 2 details the data and measurement process; Section 3 covers model development and results; Section 4 discusses implications and future steps.
The remainder of this paper is structured as follows. @sec-data...

>>>>

Polling is a commonly used tool to understand public opinion. However, it may lack accuracy due to various biases, such as social desirability bias, non-response bias, and sampling error. In this paper, we attempt to construct a model measures influencial factors to pct.

@@

@@
